Supplementary Materials for Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-24 analysis/supplementary materials/Supplementary Materials.Rmd
Update supplementary materials, remove figures, update tables

```{r, setup, echo = FALSE, message=FALSE}

library("Reproducibility.in.Plant.Pathology")
library("tidyverse")
library("pander")
library("report")
library("flextable")

@@

load(
  system.file(
    "extdata",
    "m_h1.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h1_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
```

@@

@@

## Journal Publication Model Reports

### Computational Methods

```{r journal-code, echo=FALSE}
m_f1_report %>% 
  pander()
```

### Data

```{r journal-data, echo=FALSE}
m_f2_report %>% 
  pander()
```

@@

## Year

### Computational Methods

```{r year-code, echo=FALSE}
m_g1_report %>% 
  pander()
```

### Data

```{r year-data, echo=FALSE}
m_g2_report %>% 
  pander()
```

@@

## Five-year Impact Factor

### Computational Methods

```{r if5yr-code, echo=FALSE}
m_h1_report %>% 
  pander()
```

### Data

```{r if5yr-data, echo=FALSE}
m_h2_report %>% 
  pander()
```

@@

```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_f1_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("")
```

@@

```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_f2_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("")
```

@@

```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_g1_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("")
```

```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_g2_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("")
```

```{r if-5yr-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_h1_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("")
```

```{r if-5yr-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_h2_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("")
```

>>>>

```{r, setup, echo = FALSE, message=FALSE, warning=FALSE}

library("Reproducibility.in.Plant.Pathology")
packages <- c(
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "extrafont",
  "flextable",
  "ggpubr",
  "here",
  "knitr",
  "officer",
  "officedown",
  "pander",
  "posterior",
  "report",
  "tools"
)

install.packages(setdiff(packages,
                         rownames(installed.packages())),
                 repos = "http://cran.us.r-project.org",
                 dependencies = TRUE)

invisible(lapply(packages,
                 library,
                 character.only = TRUE))

options(mc.cores = parallel::detectCores())
theme_set(theme_classic())

@@

load(
  system.file(
    "extdata",
    "m_h1.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h1_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)

knitr::opts_chunk$set(
  fig.cap.pre = "Figure S",
  tab.cap.pre = "Table S"
)
```

@@

<!---BLOCK_LANDSCAPE_START--->

@@

```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_f1_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("Full description of model fit for the effect of journal title on code availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation). The model included assignee as random effect (formula: ~1 | assignee). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions.")
```

@@

```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_f2_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("Full description of model fit for the effect of journal title on data availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation). The model included assignee as random effect (formula: ~1 | assignee). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions.")
```

@@

```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_g1_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("Full description of model fit for the effect of year of publication on code availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year). The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions.")
```

@@

```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_g2_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
    set_caption("Full description of model fit for the effect of year of publication on data availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year). The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions.")
```

@@

```{r if-5yr-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_h1_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("Full description of model fit for the effect of five year impact factor on code availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year). The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions. ")
```

@@

```{r if-5yr-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_h2_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("Full description of model fit for the effect of five year impact factor on data availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year). The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions. ")
```

<!---BLOCK_LANDSCAPE_STOP--->
